SunPy - Python for Solar Physics

### 2014-01-22 3-1-VSO.tex
fix typo in python code for vso

Querying just a single instrument
>>> lasco_query = client.query(vso.attrs.Time(tstart, tend), 
...                            vso.attrs.Instrument('lasco'))
>>> lasco_query.num_records()
40
>>> qr.show() 
Start time           End time             Source  Instrument  Type  
----------           --------             ------  ----------  ----  
2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO    LASCO       CORONA
2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO    LASCO       CORONA
...

>>>>

Querying just a single instrument
>>> lasco_query = client.query(vso.attrs.Time(tstart, tend), 
...                            vso.attrs.Instrument('lasco'))
>>> lasco_query.num_records()
40
>>> lasco_query.show() 
Start time           End time             Source  Instrument  Type  
----------           --------             ------  ----------  ----  
2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO    LASCO       CORONA
2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO    LASCO       CORONA
...
